\bf Turkish Elections and Catastrophic Events

### 2021-12-12 paper/main.tex

\if0\blind
{
  \title{\bf Turkish Elections and Catastrophic Events}
    {
}
\author{\name Deniz Tokmakoglu\\
       \addr Harris Public Policy and Department of Computer Science\\
       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub}}}
\maketitle

@@

@@

Finally, Syrian Refugee crisis increased the voter turnout by 3 percent in the affected cities. 
\newpage
\section{Appendix}
\captionsetup[table]{name=Table A}
\begin{table}[!htbp] \centering 
  \caption{Effects of a Catastrophic Event on Voter Turnout} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] &  \\ 
 & Voter Turnout \\ 
\hline \\[-1.8ex] 
 Treatment Effect & 0.640 \\ 
  & (0.650) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 200 \\ 
R$^{2}$ & 0.894 \\ 
Adjusted R$^{2}$ & 0.855 \\ 
Residual Std. Error & 2.697 (df = 146) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\if0\blind
{
  \title{\bf Turkish Elections and Catastrophic Events}
    {
}
\author{\name Deniz Tokmako{\u{g}}lu\\
       \addr University of Chicago\\Harris Public Policy and Department of Computer Science\\
       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub Page}}}
\maketitle

@@

Finally, the emergence of right wing parties and Political Islam is clearly observable in Turkish Election results. Given is the party tendencies of Municipal Election winners over the years.

\begin{figure}[h]
 \centering
\includegraphics[width=15cm]{paper/ideologies.png}
 \caption{Average Turnout for Selected Cities}
\end{figure}
\newpage

It is also obvious that this emergence occurred in the expense of left wing parties. However 2019 elections suggest that the trend started to reverse.

@@

Finally, Syrian Refugee crisis increased the voter turnout by 3 percent in the affected cities.

\section{Conclusion}

The purpose of this research was to understand the impact of regional catastrophic events on Turkish voter behaviour. While it is obvious that turnout and incumbent parties do not change right after the event, some events (especially armed conflict or war) increases the trust in the current ruling party.  While this does not establish causality; the results of this paper suggest that there definitely is a relation between the two.

\section{References}
Council on Foreign Relations. (n.d.). Conflict between Turkey and armed Kurdish groups | global conflict tracker. Council on Foreign Relations. Retrieved December 12, 2021, from https://www.cfr.org/global-conflict-tracker/conflict/conflict-between-turkey-and-armed-kurdish-groups.

Weissmann, A., &amp; Special to The Washington Post; Arnie Weissmann is a freelance writer who recently spent three months on Cyprus. (1984, January 22). Cyprus sights: Both sides now. The Washington Post. Retrieved December 12, 2021, from \\https://www.washingtonpost.com/archive/lifestyle/travel/1984/01/22/cyprus-sights-both-sides-now/413143fc-9424-40d5-b894-d1a6c64c332d/.

Platform, I. R. (n.d.). Marmara earthquake, 1999 - countries &amp; disasters. International Recovery Platform. Retrieved December 12, 2021, from \\https://www.recoveryplatform.org/countries\_and\_disasters/disaster/26/marmara\_earthquake\_1999.

Reid, K. (2021, July 13). Syrian refugee crisis: Facts, faqs, and how to help. World Vision. Retrieved December 12, 2021, from\\ https://www.worldvision.org/refugees-news-stories/syrian-refugee-crisis-facts.

Turkish Statistical Institue. (n.d.). Parlimentary and Municipality Election Database. Turkish Statistical Institute Database for Election and Justice. Retrieved December 12, 2021, from https://data.tuik.gov.tr/Kategori/GetKategori?p=adalet-ve-secim-110&amp;dil=2.

\newpage

\section{Appendix}
\captionsetup[table]{name=Table A}
\begin{table}[!htbp] \centering 
  \caption{Effects of a Catastrophic Event on Voter Turnout} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] &  \\ 
 & Voter Turnout \\ 
\hline \\[-1.8ex] 
 Treatment Effect & 0.640 \\ 
  & (0.650) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 200 \\ 
R$^{2}$ & 0.894 \\ 
Adjusted R$^{2}$ & 0.855 \\ 
Residual Std. Error & 2.697 (df = 146) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
